Constructing Statistical Deformable Models with Shape Flow

### 2015-07-16 contents/evaluation.tex
Draft Version
Updates from ShareLaTeX

%In this section we evaluate the performance of the proposed methodology in a variety of tasks. Results for 4 different experiments are reported. Experiment \ref{exp:1} compares the fitting accuracy of Dense Active Appearance Models (DAAMs) built using our methodology with respect to that of classic AAMs on the problems of non-rigid face and ear alignment in-the-wild. Experiment \ref{exp:2} investigates the impact that the Support Vector Shape representation has on the performance achieved by DAAMs on the the first experiment. Experiment \ref{exp:3} evaluates the effectiveness of the proposed methodology to build DAAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Finally, experiment \ref{exp:4} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches.

@@

In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively asses their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.

>>>>

%In this section we evaluate the performance of the proposed methodology in a variety of tasks. Results for 4 different experiments are reported. Experiment \ref{exp:1} compares the fitting accuracy of Dense Active Appearance Models (DAAMs) built using our methodology with respect to that of classic AAMs on the problems of non-rigid face and ear alignment in-the-wild. Experiment \ref{exp:2} investigates the impact that the Support Vector Shape representation has on the performance achieved by DAAMs on the the first experiment. Experiment \ref{exp:3} evaluates the effectiveness of the proposed methodology to build DAAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Finally, experiment \ref{exp:4} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches

@@

In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
